Typing a linear \picalc

### 2020-02-24 paper/paper.tex
Proved subject congruence!!
Get Quantifiers module out, clean up imports
Add some notes on multiplicity algebras
Draft an abstract

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Typing a linear \picalc}
\author{Uma Zalakain}{University of Glasgow, Scotland}
       {uma.zalakain.1@research.gla.ac.uk}{https://orcid.org/0000-0002-3268-9338}{}
\author{Ornela Dardha}{University of Glasgow, Scotland}
       {ornela.dardha@glasgow.ac.uk}{https://orcid.org/0000-0001-9927-7875}{}
\authorrunning{U. Zalakain and O. Dardha}
\Copyright{Uma Zalakain and Ornela Dardha}
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10003753.10003761.10003764</concept_id>
<concept_desc>Theory of computation~Process calculi</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[300]{Theory of computation~Process calculi}
\keywords{pi calculus, linear, types, concurrency}
\supplement{\url{https://github/umazalakain/typing-linear-pi}}
\acknowledgements{I want to thank \dots}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{abstract}
  We present the syntax, operational semantics, and typing rules for a \picalc{} with linear and shared types. We use leftover typing \cite{} to encode our typing rules. We build framing and weakening proofs that we then use to prove subject congruence and subject reduction.
\end{abstract}

@@

Intensional (correct by construction) vs extensional

same syntax and semantics, different typing rules

@@

unique quirks: multiple multiplicities per variable, shared types

@@

strings to maybe de Bruijn

@@

@@

$\inf$ and $\mathbb{N}$ as generalisations

properties of the underlaying monoid

\subsubsection{Total definition}

\subsubsection{Partial definition}

partial vs total

@@

@@

Decidable typechecking

Proof of progress

Product types

Sum types

Encoding of session types

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Typing a linear \picalc}
\author{Uma Zalakain}{University of Glasgow, Scotland}
       {u.zalakain.1@research.gla.ac.uk}{https://orcid.org/0000-0002-3268-9338}{}
\author{Ornela Dardha}{University of Glasgow, Scotland}
       {ornela.dardha@glasgow.ac.uk}{https://orcid.org/0000-0001-9927-7875}{}
\authorrunning{U. Zalakain and O. Dardha}
\Copyright{Uma Zalakain and Ornela Dardha}
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10003753.10003761.10003764</concept_id>
<concept_desc>Theory of computation~Process calculi</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[300]{Theory of computation~Process calculi}
\keywords{pi calculus, linear, types, concurrency}
\supplement{\url{https://github/umazalakain/typing-linear-pi}}
\acknowledgements{I want to thank \dots}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{abstract}
  We present the syntax, operational semantics, and typing rules of a \picalc{} with linear and shared types.
  We abstract over types (using \emph{shapes} to untangle usage contexts from typing contexts) and generalize the algebras on multiplicities (using indexed sets of \emph{partial commutative monoids}).
  We use leftover typing \cite{Allais2018a} to encode our typing rules in a way that propagates linearity constraints into process continuations.
  We provide framing, weakening and strengthening proofs that we then use to prove subject congruence.
  We show that the type system is stable under substitution and prove subject reduction.

  This formalization has been fully mechanized with Agda and is available at \url{https://github.com/umazalakain/typing-linear-pi}.
\end{abstract}

@@

extensional typing rules for a given syntax and operational semantics

@@

multiple multiplicities per variable

multiple multiplicity types

@@

allows to ignore alpha conversion, or proofs of inequality between strings

strings to maybe de Bruijn, names can be kept in context as well, just not doing it

@@

\subsection{Structural congruence}

congruence relationship indexed by recursive tree

\subsection{Reduction}

@@

Generalisation over indexed sets of \emph{partial commutative monoids}

given two multiplicities, the third is uniquely determined. this is better modelled through a function rather than an inductive type.

@@

\subsection{Strengthening}

\subsection{Swapping}

\subsection{Substitution}

@@

\begin{description}

\item [Soundness and completeness with respect to an alternative formalization.]

\item [Proof of progress]

\item [Product types]

\item [Sum types]

\item [Decidable typechecking]

\item [Encoding of session types]

\end{description}
